Growth model analysis

### 2018-02-02 manuscriptAnalysis/MS_Analysis.Rmd
added sampleInterval to gr in model

rm(dddG,ddG,dG,mcmcProcessed)
```

@@

ggplot(d, aes(year,nAllFishBySpeciesP)) +
  geom_point(aes(color=species)) +
  geom_line(aes(color=species)) +
   geom_line(  aes(year,nAllFishP) ) +
  labs( x = "Year", y = "Estimated count") +
#  ylim(0,2500) +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
```

@@

ggplot( grIndRE[[1]], aes(value) ) +
  geom_freqpoly(binwidth = 0.0025) +
  geom_freqpoly(aes(value), color = "brown", binwidth = 0.0025, data = grIndRE[[2]]) +
  geom_freqpoly(aes(value), color = "lightblue", binwidth = 0.0025, data = grIndRE[[3]])

>>>>

rm(dddG,ddG,dG,mcmcProcessed)

load("D:/projects/linkedModels/data/cd_west_1997.RData")
```

@@

ggplot(d, aes(year,nAllFishBySpeciesP)) +
  geom_point(aes(color=species)) +
  geom_line(aes(color=species)) +
   geom_line(  aes(year,nAllFishP) ) +
  labs( x = "Year", y = "Estimated count") +
#  ylim(0,2500) +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
```
```{r raw growth rates}

cdMeans <- cd %>%
  mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
  group_by(species,riverOrdered,season) %>%
  summarize( meanGr = mean( gr, na.rm = TRUE ),
             sdGr = sd( gr, na.rm = TRUE )) %>%
  mutate( meanGrUp = meanGr + sdGr,
          meanGrDn = meanGr - sdGr
          )

pd <- position_dodge(0.05) # move them .05 to the left and right

# all three species
ggplot( cdMeans %>% filter(riverOrdered == 'west brook'), aes(season, meanGr, color = species) ) +
  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
  geom_point( size = 2 ) +
  geom_line()

cd$isYOY <- ifelse( cd$ageInSamples <= 3, 1, 2 )
cdMeansByisYOY <- cd %>%
  mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
  group_by(species,riverOrdered,season,isYOY) %>%
  summarize( meanGr = mean( gr, na.rm = TRUE ),
             sdGr = sd( gr, na.rm = TRUE )) %>%
  mutate( meanGrUp = meanGr + sdGr,
          meanGrDn = meanGr - sdGr
          )

# all three species
ggplot( cdMeansByisYOY %>% filter(riverOrdered == 'west brook'), aes(season, meanGr, color = species) ) +
  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
  geom_point( size = 2 ) +
  geom_line()+
  facet_wrap(~isYOY)

# bkt only
pdBKT <- position_dodge(0.05) # move them .05 to the left and right
ggplot( cdMeans %>% filter(species=='bkt'), aes(season, meanGr, color = riverOrdered) ) +
  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pdBKT) +
  geom_point( size = 3 ) +
  geom_line( size = 1 ) +
  facet_wrap(~isYOY)

@@

ggplot( grIndRE[[1]], aes(value,..density..) ) +
  geom_freqpoly(binwidth = 0.0025) +
  geom_freqpoly(aes(value), color = "brown", binwidth = 0.0025, data = grIndRE[[2]]) +
  geom_freqpoly(aes(value), color = "lightblue", binwidth = 0.0025, data = grIndRE[[3]])
